% Acknowledgments. 
%
% \SVN $Revision: 840 $
% \SVN $Author: sgordon $
% \SVN $Date: 2014-05-12 13:39:14 +0700 (Mon, 12 May 2014) $
% \SVN $URL: https://sandilands.info/svn/Common/Styles/siitthesis/ack.tex $

This thesis is the end of my long journey obtaining a doctorate degree in Engineering and Technology. 
I can honestly state that it would not have been possible without the support from several people.

First of all, I would like to express my sincere gratitude to my advisor Assoc. Prof. Komwut Wipusitwarakun for his continuous support of my Ph.D. study and research, for his patience, motivation, enthusiasm, and immense knowledge.
At every step of my thesis, he guided me with his profound knowledge, insight and wisdom.
I would like to express my deep gratitude to him for being such a great advisor. 

Besides my advisor, I would like to thank the rest of my thesis committee: Assoc. Prof. Steven Gordon, Asst. Prof. Prapun Sukompong and Asst. Prof. Somsak Kittipiyakul, for their encouragement, insightful comments, and hard questions. I also would like to express my appreciation to my external examiner, Prof. xxx xxxx, for his useful suggestions and helpful comments. 
I am thankful for all faculty members in the school of Information and Computer Technology, SIIT, for their support, valuable comments and suggestions on the research.

I also would like to thank to my colleague in Information Technology of SIIT and Defence Technology Institute (DTI), for stimulating discussions and all the fun we had studying together. 
I appreciate their efforts in helping me solving several problems I faced through this thesis work.
Thanks for their concern, mind power and encouragement all the time.
Especially my supervisor at DTI, Asst. Prof. Tawiwat Veeraklaew, who inspires me and also recommended me to pursue my Ph.D. at SIIT.

Finally, my deep gratitude goes to my family, my mother and sister.
I am very grateful to them for standing by me in everything I have done and giving me whatever they can.
They have always provided me continuous support, encouragement and their love.
I believe that nothing would be possible without the presence of them and the peaceful family environment they provided me during my life.
Even though my father already passed away but he had always been my greatest teacher who inspire me about higher education. 
I would like to dedicate this thesis to them.