\chapter{List of Publications}
\label{app1}
% \SVN $Revision: 840 $
% \SVN $Author: sgordon $
% \SVN $Date: 2014-05-12 13:39:14 +0700 (Mon, 12 May 2014) $
% \SVN $URL: https://sandilands.info/svn/Common/Styles/siitthesis/appendixA.tex $


\paragraph{International Journals}

\begin{itemize}
\item Jiradett Kerdsri, Komwut Wipusitwarkun, "Dynamic Rendezvous based Routing Algorithm on Sparse Opportunistic Network Environment", \textit{International Journal of Distributed Sensor Networks}, Vol. x, No. xx, pp. xx-xx, 2015 (in ISI, impact factor=0.923)
(To appear)
  \item Jiradett Kerdsri, Komwut Wipusitwarkun, "DORSI: Data-wise Opportunistic Routing with Spatial Information", \textit{JCIT: Journal of Convergence Information Technology}, Vol. 8, No. 13, pp. 91-103, 2013 (in SCOPUS)
\end{itemize}


\paragraph{International Conferences}

\begin{itemize}
\item Jiradett Kerdsri, Komwut Wipusitwarkun, "Rendezvous Based Routing in Opportunistic Networks" \textit{The Third International Conference on Informatics Engineering and Information Science (ICIEIS2014)}, pp.121-126, 22-24 Sep. 2014
\item Jiradett Kerdsri, Komwut Wipusitwarkun, "Data-wise Routing in Virtualization Environment (DRIVE) with multiple level of security for tactical network" \textit{2012 IEEE/SICE International Symposium on System Integration (SII)}, pp.933-938, 16-18 Dec. 2012
\item Jiradett Kerdsri, Komwut Wipusitwarkun, "Network virtualization for military application: Review and initial development of conceptual design", \textit{14th International Conference on Advanced Communication Technology (ICACT)}, pp.61-66, 19-22 Feb. 2012  
\end{itemize}